A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-24 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added chitra reference

While not agent based, Chitra et al. \cite{chitra2019agent} effectively use discrete event simuation to

Agent based systems could help evaluate trends in behavior related to
various system parameters. They may not however, accurateley represent 
actual system performance.

Discuss levels of complexity, with citations. Why greater complexity may
not get you much more insight.

>>>>

While not agent based, Chitra et al. \cite{chitra2019agent} effectively use discrete event simuation to provide
quantitative estimates of how economic incentives affect security. They use a custom simulation
environment to simulate Kadena's Chainweb, and provide insights into how simulation can guide
and optimize protocol development in a variety of contexts.

Discuss levels of complexity, with citations. Why greater complexity may
not get you much more insight. (ask Shruti?)
